Arrows for Parallel Computations

### 2017-10-24 paper/content/benchmarks.tex
remarks done (oleg reread), only abstract missing

Continuing, the results of the \jacobitest in \ref{fig:bench-jacobi-dist} are as follows:

Not pictured: difference between Eden and PArrows with 4253

@@

\mbcomment{FIXME: redo this test with $2^{44497}$}

@@

In our distributed memory tests on the full grid we were unable to detect any performance deficiencies of PArrows \wrt Eden that were above of the error margin.
In our distributed memory tests on the full grid the difference between PArrows and Eden was always below the error margin.

>>>>

Continuing, the results of the \jacobitest (MPI only) in Fig.~\ref{fig:bench-jacobi-dist} are as follows:
The program does not seem to scale well beyond 16-32 tasks with input $2^{3217}-1$. Because of this, we also ran tests with input $2^{4253}-1$, but only for the 128 and 256 cores because of the long running time. For demonstration purposes in Fig.~\ref{fig:bench-jacobi-dist}, we chose a simulated speedup of 22 for 128 cores. For 256 cores, this results in a superlinear speedup of \~122.63, which suggests an IO limitation for this big input that is somewhat mitigated by adding more cores.

We once again compare the Eden version with the PArrrows version in Fig.~\ref{fig:bench-jacobi-dist}. We see similar behaviour to the MPI version of the \rmtest: The difference once again almost always remains within the bounds of the error bar of the measurement.

Not pictured are the slightly bigger differences between Eden and PArrows for the larger input of $2^{4253}-1$: For 128 and 256 cores the differences are -1005.18\seconds and -94.33\seconds in favour of Eden. This maximum of 12.27\% slower PArrows runtime, however, was still in the (quite big) error bar of our measurements.

@@

@@

In our distributed memory tests on the full grid we were unable to detect any performance deficiencies of PArrows \wrt Eden that were above of the error margin.
In our distributed memory tests on the full grid the difference between PArrows and Eden was always below the error margin if PArrows performed worse. Even the biggest difference of 12.27\% in the \jacobitest for input $2^{4253}-1$ and 128 cores remained in line with these findings.
